### 2025-07-01 machine-learning.qmd
20250701 - heading
20250701 - tweaks

@@

gp_data_qb <- gpboost::gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"]) #use mean-centered variable and add mean back afterward

>>>>

### Create New Data Object for Merging with Later Predictions {#sec-newDataObject}

@@

gp_data_qb <- gpboost::gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"]) # could use mean-centered variable and add mean back afterward

### 2025-07-01 multiple-regression.qmd
20250701 - tweaks

ggplot(
  quadraticTermsRegressionModelStandardized_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Regression Coefficients with 95% CI",
    x = "Predictor",
    y = "Standardized Coefficient Estimate") +
  theme_minimal()
```

>>>>

ggplot(
  quadraticTermsRegressionModelStandardized_tidy,
  aes(
    x = term,
    y = estimate)) +
  geom_point() +
  geom_errorbar(
    aes(
      ymin = conf.low,
      ymax = conf.high),
    width = 0.2) +
  coord_flip() + # flip axes for readability
  labs(
    title = "Standardized Regression Coefficients with 95% CI",
    x = "Predictor",
    y = "Standardized Coefficient Estimate") +
  theme_minimal()
```
